Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
fixing tables

In our research objective we have to classify the code smells related to the usage of features toggles. One such code smell is to identify the distribution of the same toggles flag among various sources files, we have named this as “TOGGLE SPREAD”. This indicates the loose cohesion of a feature. This study is used to identify the features from the source code using Aspect oriented programming.\\

Pierre Genevès and Nabil Layaïda~\cite{geneves2010eliminating} studied how to detect and remove dead code from Xquery programs. They propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program. XQuery is a query and functional programming language basically takes one (or possibly several) XML document as input, performs some computation based on its tree view, and finally outputs a result in the form of another XML document. The core of the XQuery language is composed of XPath expressions that make it possible to navigate in the document tree and extract nodes that satisfy some conditions. They use two methodology \textbf{Path-Error Detection} and \textbf{Static Code Refactoring and Highlighting}. In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema. If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.\\

@@

\begin{table}[ht]
\caption{Dead Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{7cm}|}
 \hline\hline
 Description & This smell is present if the toggle repository does not possess the information about the toggle flag, but the source code is still found to use the flags to encapsulate code blocks. \\ \hline
 Example & 
 \begin{lstlisting}
if(switches::toggle1){
    Do something
}else{
    Do something else
}
 \end{lstlisting}
  \\ \hline

@@

 \\ \hline
\end{tabular}
\label{table:chrome-dir-data}
\end{table}

\begin{table}[ht]
\caption{Dead Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{7cm}|}
\hline\hline
 Description & This smell is observed when one toggle flag is dependent on the state of one or more other toggle flags. \\ \hline

 Example & There are different patterns of this code smell similar to ``Message Chains''
 \begin{enumerate}
 \item{A variable might be used to store the state of the dependent toggles and will be used as a short circuit while checking the state of the actual feature flag.
 \begin{lstlisting} 
 boolean showF1Menu = ToggleService.isOn(“SHOW_F1_MENU”);

 if(showF1Menu && ToggleService.isOn(“SHOW_F1_F11_MENU”) {
 ….

 }
 \end{lstlisting}
 }

@@

 Detection & This smell could be detected using the following approach.\\
 \begin{enumerate}
 \item{In order to identify potential positive instances of this smell, the detector could use trained patterns using a mathematical model like BLR(Binary Logistic Regression).}
 \item{Or simple level count could be used to identify the smell. Say for example if the number of nested toggles levels is greater than 2 then there is a possibility of the presence of this code smell.}
 \item{Also the detector can be enhanced to identify that there is a common master toggle used for the most of the nested toggles and could be prevented in identifying false smells.}
 \end{enumerate}

\subsection{Mix of Compile time and run-time toggles)}

\begin{table}[ht]
\caption{TOGGLE\_MIX}
\centering
\begin{tabular}{|p{1.5cm}|p{7cm}|}
 \hline\hline
 Description & This smell is observed when the source code uses multiple techniques to manage toggles. One such usage is to combine compile time (\#define, \#ifndef) along with run time toggles.  \\ \hline

 Example & 
 \begin{lstlisting}
 //Location: /chrome/app/chrome_main_delegate.cc (Taken from Google chrome)
#if defined(OS_MACOSX)
// Mac needs them too for scrollbar related images and for sandbox
// profiles.
#if !defined(DISABLE_NACL)
process_type == switches::kNaClLoaderProcess ||
#endif
process_type == switches::kPpapiPluginProcess ||
process_type == switches::kPpapiBrokerProcess ||
process_type == switches::kGpuProcess ||
#endif
process_type == switches::kRendererProcess ||
process_type == switches::kUtilityProcess;
}
 \end{lstlisting}

@@

 Detection & TBD \\ \hline
\end{tabular}
\label{table:chrome-dir-data}
\end{table}

@@

\begin{table}[ht]
\caption{TOGGLE\_STABLE}
\centering
\begin{tabular}{|p{1.3cm}|p{7cm}|}
 \hline\hline
 Description & This smell is observed when the feature has received enough feedback from the production environment and has been observed stable through several releases and became permanent in the product. However the code for the features are still running with the toggle check.  \\ \hline

>>>>

In our research objective we have to classify the code smells related to the usage of features toggles. One such code smell is to identify the distribution of the same toggles flag among various sources files, we have named this as ``TOGGLE SPREAD''. This indicates the loose cohesion of a feature. This study is used to identify the features from the source code using Aspect oriented programming.\\

In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema. If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.\\

@@

\begin{table}[!h]
\caption{Dead Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is present if the toggle repository does not possess the information about the toggle flag, but the source code is still found to use the flags to encapsulate code blocks. \\ \hline
 Example & 
 \begin{lstlisting}
if(switches::toggle1){
    Do something
}else{
    Do something else
}
 \end{lstlisting}
  \\ \hline

@@

 \\ \hline
\end{tabular}
\label{table:toggle-dead}
\end{table}

\subsection{TOGGLE\_NEST (Nested Toggles)}
\begin{table}[!h]
\caption{Nested Toggle Smell}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
\hline\hline
 Description & This smell is observed when one toggle flag is dependent on the state of one or more other toggle flags. \\ \hline

 Example & There are different patterns of this code smell similar to ``Message Chains''
 \begin{enumerate}
 \item{A variable might be used to store the state of the dependent toggles and will be used as a short circuit while checking the state of the actual feature flag.
 \begin{lstlisting} 
 boolean s = functionX();

 if(s && functionX()){
 ...
 }
 \end{lstlisting}
 }

@@

\end{tabular}
\label{table:nested-toggle}
\end{table}

\subsection{TOGGLE\_MIX (Mix of compile-time and run-time toggles)}

\begin{table}[!h]
\caption{TOGGLE\_MIX}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is observed when the source code uses multiple techniques to manage toggles. One such usage is to combine compile time (\#define, \#ifndef) along with run time toggles.  \\ \hline

 Example & 
 \begin{lstlisting}
#if
process_type == switches::kNaClLoaderProcess ||
#endif
process_type == switches::kPpapiPluginProcess ||
process_type == switches::kGpuProcess
#endif
}
 \end{lstlisting}

@@

\end{tabular}
\label{table:mix-toggle}
\end{table}

@@

\begin{table}[!h]
\caption{TOGGLE\_STABLE}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is observed when the feature has received enough feedback from the production environment and has been observed stable through several releases and became permanent in the product. However the code for the features are still running with the toggle check.  \\ \hline
